\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-12 docs/paper.tex

Many relevant studies have been conducted to show the vulnerability of IDN and provide possible solution to mitigate IDN homograph attack.
In 2001, Evgeniy Gabrilovich and Alex Gontmakher has proved the feasibility of such attack based on the vulnerability of Unicode in \textit{The Homograph Attack}~\cite{theHomoAttack}.
In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
His method of defense mainly target at regular users who do not necessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing URL users would be aware of malicious website.
Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
They proposed an advanced method based on URL components and spell checking functionality of search engine.
In this method, an URL would be divided into several components, namely, base name, sub-domains, path domain, brand name.
Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the URL will be counted as suspicious.
The major browsers have their own IDN policies to defend against IDN homograph attack.
Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
IE displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
Firefox uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
Opera shows IDN only for whitelisted TLDs.
Safari has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.

>>>>

Many relevant studies have been conducted to show the vulnerability of IDN and provide possible solution to mitigate IDN homograph attack.
In 2001, Evgeniy Gabrilovich and Alex Gontmakher has proved the feasibility of such attack based on the vulnerability of Unicode in \textit{The Homograph Attack}~\cite{theHomoAttack}.
In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
This method check each character in an url seperately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multiscript is detected by means of scripts block\footnote{\url{http://www.unicode.org/reports/tr24/}}.
His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.
Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
They proposed an advanced method based on url components and spell checking functionality of search engine.
In this method, an url would be divided into several subterms, namely, base name\footnote{The primary domain name as registered at the registrar}, subdomain\footnote{A part of the primary domain}, path domain\footnote{A subfolder of the url}, brand name\footnote{A brand name that occurs in a url}.
Their algorithm is based on the following characteristics on different subterms of url:
\begin{itemize}
  \item Base name: Phisher cannot register the original domain but can only register mispelling or homograph domain name because the original one is often registered ahead by the company.
  \item Subdomain: Phisher can prepend subdomain to the primary domain being attacked to fool users into thinking that they are on the real domain. One example would be \url{http://us.battle.net.loginaccoutbattle.net/login/en/login.html}.
  \item Path domain: Phisher sometimes place a second domain as a subfolder of the url path, usually right after the primary domain name, for instance, \url{http://piasel.altervista.org/www.paypal.com/new/paypal/intl/update}.
  \item Brand name: There are cases that only the brand name is inserted somewhere in the URL to fool users.
\end{itemize}
Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the url will be counted as suspicious.
By splitting a url into these subterms, this method cover almost all possible cases of fake url or domain name.
However, this mechanism is based on the search engine for return spelling suggestion and as a result, it does not play well when it is used as sole detection.
The major browsers have their own IDN policies to defend against IDN homograph attack.
Google Chrome, starting with Chrome 51, will display punycode if certain tests fail on the input url.
These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
Opera\footnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
Safari\footnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
